**Density Dependence**

### 2023-02-09 Rmd/ddMac.Rmd
cleaning up

```{r, check2}
save(om2,file="~/Desktop/tmp/t.RData")
load("~/Desktop/tmp/t.RData")
ggplot(model.frame(FLQuants(om2[,dim(m(om2))[2]],"Biomass"=biomass,"Yield"=catch)))+
  geom_line(aes(Biomass,Yield),col="red")+
  geom_line(aes(Biomass,Yield),data=model.frame(FLQuants(om[,dim(m(om))[2]],"Biomass"=biomass,"Yield"=catch)))
```

>>>>

```{r, check2}
# save(om2,file="~/Desktop/tmp/t.RData")
# load("~/Desktop/tmp/t.RData")
ggplot(model.frame(FLQuants(om2[,dim(m(om2))[2]],"Biomass"=biomass,"Yield"=catch)))+
  geom_line(aes(Biomass,Yield),col="red")+
  geom_line(aes(Biomass,Yield),data=model.frame(FLQuants(om[,dim(m(om))[2]],"Biomass"=biomass,"Yield"=catch)))
```
